A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-18 0_reviewer_response.tex

%$W(n, r)$ and $L(n, r)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}
}{}

\revise{
The following restrictions hold:
\begin{enumerate}
	\begin{minipage}{\columnwidth}
	\setlength\intextsep{0pt}
	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
	%\caption{
	%%Transition ends (magenta and pink) shouldn't cross each other.
	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
	%}
	\label{transition_placement}
	\end{wrapfigure}
	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
\end{minipage}
\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
\item For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
\end{enumerate}
}{}

\revise{}{
\begin{definition}\label{beading_scheme_definition}
A beading scheme is defined by the quatization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
\end{definition}
}
% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section 3.4 Smooth transitions

\revise{}{
For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$.
We further ensure
that beads don't overlap,
that beads are extruded from the center of where they end up
and that odd bead counts produce a single polyline toolpath exactly in the center
by determining the bead locations from the widths:
}
\begin{align*}
L(n,r)_i = 
\begin{cases}
-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
r & \text{ if } i =  \frac12 (n -1) \\
%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

% \subsection{Beading schemes}
We introduce several beading schemes which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
We also introduce new beading schemes which produce toolpaths with less extreme widths compared to techniques from existing literature.

\revise{
A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
L(n,r)_i = 
\begin{cases}
-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
r & \text{ if } i =  \frac12 (n -1) \\
%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\\
\begin{array}{rlrl}
t_\text{beading} &= w^* 
&
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
\\
t(n) &= w^*
&
d_\text{max}^\text{unmarked} &= w^*
\\
t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
&
d^\text{discretization} &= \SI{0.2}{\milli\meter}
\\
\alpha_\text{max} &= \SI{135}{\degree} 
&
d_\text{max}^\text{intersection} &= \SI{75}{\percent}
\end{array}
%\end{align*}
%\begin{align*}
\end{align*}
}{}

\revise{
The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.
The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $R(v) = \nicefrac12 n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
}{}

\paragraph{Uniform beading scheme}
[\dots]
\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.

\paragraph{Constant bead count}
[\dots]
Additionally in order to emulate their definition of ``branches'' we mark all ST edges \revise{}{($\alpha_\text{max} = \SI{0}{\degree}$) and }we unmark the outer edges connected to the outline shape in a separate algorithm.
[\dots]

\paragraph{Centered}
[\dots]
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
}
\paper{5.3 Limitations, second paragraph}
{
\revise{}{
The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} \approx \SI{0.4}{\milli\meter}$ long segments
and under-/overfill areas of $\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right) \approx \SI{0.05}{\milli\meter\squared}$.
However, future work might be aimed at reducing under-/overfill in regions with a low bisector angle without the introduction of short single polyline extrusion segments.
If the over-/underfill problem is also solved for non-significant regions we might be able to increase $\alpha_\text{max}$ and reduce the discontinuity introduced by short extrusion segments.
}
}

@@

\Que{
Is this approach generalizable to sparse infill? It is very common in FDM to use a sparse infill and only use dense fill on surface regions.
}
\Ans{
The goal of sparse infill is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
See our response to 3.2.
}

\Que{
If this is used for outer surface, what are the implications on the surface quality in comparison to other approaches? 
}
\Ans{
The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
See our response to question ~\ref{s5_prints}.
}
\commits{
6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)
}
\paper{Abstract}{
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
}

@@

\Que{
I think Figure 13 should be replaced with a table. 
}
\Ans{
Indeed. Done.
}
\commits{735762b1e7daf31ae4465bf288ef867ded7da095}
% commit only now shows table

\Que{
In text, some references are missing, such as first sentence of “Outer bead” paragraph in Section 4 (Moesen et al [?]), first sentence of “Constant bead count” (Ding et al [?]) paragraph in Section 4 etc. 
}
\Ans{
We cannot reproduce this typesetting bug. Please inform the proofing department to take extra care of these references when preparing this manuscript for publication.
}

\Que{
Evaluation in the results section is overall good but it is not clear what are the implications of the presented approach on the complete 3D result. A discussion on this would be helpful.
}
\Ans{
We have discussed several implications of our method and in a sense they are all implications on the complete 3D result.
In our revision we address several new implications;
we address the influence of layers in each other and the implications of underfill on stiffness.
We hope that these suffice.
% See answers to question~\ref{contributions}
}
\commits{
3b13960e15c07f484ab641a2d941f6086eda571c describe implications on full model (reviewer 3.12)
dd293c060baae147ad1a217cf6ab68d8c4cb00c8 lil reformulation in conclusion (reviewer 3.12)
2f83d078036e267195431a7b077201eef0352e19 % influence of layers on back pressure
}
\paper{6. Conclusion and future work, last paragraph}{
\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
}
\paper{5.4.1 Back pressure compensation}
{
\revise{}{Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.}
}

\Que{
What are the limitations of the presented algorithm? I do not see any discussions of the limitations of the algorithm.
}
\Ans{
The limitations are now handled in a new section, together with an analysis of the relation between feature size and bead width range.
%Some more general limitations are discussed in the Conclusions section.
}
\commits{
5b8c5971d606089754ba118560e51ec6d7dfda0b % extrusion width range considerations
ecf99f47dadf9973f527c1d471d662d87f6a5f51 move Theoretical considerations to 5.3 and discuss limitations (reviewer 3.13)
}
\paper{5.3 Limitations}
{
\revise{}{
Another limitation of our method is that in a location $v$ with locally maximal $R(v) \approx (i + \nicefrac12) w^*$ the odd bead count will result in a single polyline extrusion segment consisting of only a single point.
This can be viewed in the bottom right of \cref{TEST_InwardDistributed_accuracy} for example.
In order to print such a dot, we make it into a \SI{10}{\micro\meter} long extrusion segment, with an altered width such that the total volume remains correct.
A more principled way of dealing with such a situation remains future work.

Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
}
}

@@

Improvements to abstract.
\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
\paper{Abstract}{
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
}

Fix double header of References.
\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}

Added patent notice and url to open source implementation.
\commits{ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a}
\paper{Intro}{
\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
}

Lil
\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172
1662d3c4c3aa977bddd730ac59f1bc874b9eb574 % -''See ``
b108d7de4f1e1e9676d45cf24eea263af6b8b9c7 % width => widths
9d9f02edc43689c0970a74118e44a196cc11c729 % typos
}

Our department has changed its name:
\commits{
442a5df5a4f27f1ce94a5ef298a1f7bcc3df934d
}

Removed confusing red parts from beading figure:
\commits{
1196bad1c2bf4fb41e7d28985938cfe678384e5a
}

### 2020-01-16 0_reviewer_response.tex

	% Revise macro (usage: \revise{old}{new})
	% Version a) First arg red and striked out, second argument green
	%\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}\noindent{\color{blue}{#2}}}
	%\newcommand{\revise}[2]{{\textcolor{red}{#1}}{\textcolor{blue}{#2}}}
	\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
	% Version b) First arg ignored, second argument green
	%\newcommand{\revise}[2]{\textcolor{blue}{#2}}
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}

	\usepackage{alltt}

	\newcommand{\question}[1]{{\bf#1}}
	\newcommand{\todo}[1]{\par\noindent{\bf \color{orange}#1}}
	\newcommand{\commits}[1]{{\bf\begin{alltt} {#1}\end{alltt}}}
	\renewcommand{\commits}[1]{}
	\newcommand{\response}[1]{{#1}}
\newcommand\paper[2]{\par changes to \emph{#1} --- ``#2'' }
%\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }

\newcommand\Summary[1]{
   \noindent\emph{Summary.} {\bf#1}\par}

@@

\end{frontmatter}

We are very grateful for the feedback and contributions of the reviewers.
We feel that their feedback has provoked a leap forward in quality of the presented manuscript.
We have addressed the reviewers' feedback and made changes to the text.
Some of feedback has provoked large and structural changes to the manuscript;
we list the most important changes here:

\begin{enumerate}
\item We have more clearly distinguished our work from existing methods.
\item We have introduced extensions to the beading schemes:
\begin{enumerate*}
\item the widening meta-scheme is extended with a minimal feature size, in order to allow for a fair comparison between the various techniques 
and
\item a limiting meta-scheme is introduced which only generates the outer $N$ insets, so that the framework can readily be combined with the direction-parallel strategy in a manner common in FDM.
\end{enumerate*}
\item The results have been recalculated accordingly.
\item We have developed a new manufacturing method which doesn't rely on custom machinery and which clearly shows the feasibility of adaptive bead width.
\item We have computed fabrication time results.
\item \todo{We have added a video animation explaining the union of cones approach in an intuitive manner.}
\end{enumerate}

\Que{Example text by reviewer.}
\Ans{Example response.}
\paper{Section name}{
Remaining text, followed by 
\revise{outdated text in manuscript}{new text in manuscript}
}
\todo{Comment for us internally (should be removed before this letter is sent).}
\commits{123commit-hash}

\section{Reviewer 1}
\Summary{
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed. 
}
\Ans{
We agree with this summary, although it does not stress the contribution of a novel beading scheme in the framework which improves on the state of the art.
We have made various changes to highlight those as separate contributions.
}

@@

\Que{
In Fig. 17(b), where is the curve for the ”uniform” case?
}
\Ans{
We've added it back in.
Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve is not really informative.
}
\commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}
\paper{Fig. 17b}{
\todo{Figure now has the uniform curve}
}

\section{Reviewer 2}
\Summary{
The paper is generally well written with clear illustrations. 
}
\Ans{
Thank you.
}

@@

\Que{
At the same time, the scheme can potentially result in trajectories with many inflection points - this is slow and demanding for the machine. 
}
\Ans{
We have added statistics on fabrication time and discussed our findings.
See our response to 1.3.
}

\Que{
Finally, the examples provided depict the results obtained by the authors by "emulating" other techniques, but not with the actual results produced by the other techniques. While the reason behind this choice is easy to guess, it weakens the effectiveness of the claims. Adding careful discussions/extensions to support these questions would make the paper stronger.
}
\Ans{
We've added a paragraph to section 5.3. Limitations, which discusses these emulation limitations.
}
\commits{
639dccad8e97fa1f0bdbb28e16b64f587572792d % paragraph in limitations
}
\paper{5.3 Limitations}
{
\revise{}{
Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
}
}

\section{Reviewer 3}
\Summary{
Paper is well written. It is mostly easy to follow but overall, I find the the contributions somewhat incremental and the motivation not convincing. The paper mostly feels like a technical report. I am not sure if the methods overall teach enough to the researchers in the field to open up new research possibilities. My specific comments are below: 
}
\Ans{
Thank you for your feedback.
